mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-05 Draft1.Rmd
errors
1 sentence

## Subscripts and Superscripts

@@

>>>>

## Subscripts and Superscripts
Secondly, \pkg{mathml} allows also for the display of subscripts, superscripts and their combination.

@@

## Errors

An additional feature that this package offers is related to its application in educational scenarios. The functions here reported are intended to identify and highlight possible errors that students make, as well as provide the correct answer for the task.
